---
title: "p8105_hw5_kb2977"
author: "Francois Ban"
date: "11/3/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)
library(readr)
library(ggridges)
library(purrr)
library(httr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
```

##Problem 1

####Part 1: Creating tidy dataframe

Below I've created a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time.

```{r patient_data_df}
patient_data_df = 
  data_frame(patient_id = list.files(path = "./data"),
            csv_file = str_c(path = "./data/", patient_id)) %>% 
  mutate(new_var = map(csv_file, read_csv)) %>% 
  unnest() %>% 
  janitor::clean_names() %>% 
  gather(key = week, value = obs, week_1:week_8) %>% 
  separate(week, into = c("remove_1", "week"), sep = "_") %>% 
  separate(patient_id, into = c("arm", "patient_id"), sep = "_") %>%
  separate(patient_id, into = c("patient_id", "remove_2"), sep = ".c") %>% 
  mutate(patient_id = str_c(arm, patient_id, sep = "_")) %>% 
  select(-remove_1, -remove_2, -csv_file)
```

####Part 2: Spaghetti plot

Below is a spaghetti plot showing observations on each subject over time.

```{r plot_data}

plot_1 = patient_data_df %>% 
  ggplot(aes(x = week, y = obs, group = patient_id, color = arm)) +
  geom_line() +
  labs(title = "Observations over Time for Each Subject",
       x = "Time in Weeks",
       y = "Observations") + 
  viridis::scale_color_viridis(name = "Study Arm", discrete = TRUE)
plot_1

```

Overall, the experimental study arm has bigger values than the control arm. As time goes on, the difference between the two study arms increases. At week 1, the observations overlab between the two study arms whereas by week 8, the observations between two arms do not overlap.

##Problem 2

####Part 1: Reading in raw data and short description: 

```{r homicide_data}
homicide_data = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")
```

The homicide data consists of the following variables: `r ls(homicide_data)`. There are `r nrow(homicide_data)` observations. Some variables are related to victim information and some variables are related to the location of the homicide.

####Part 2: Creating city_state variable

Below I've created a city_state variable (e.g. “Baltimore, MD”) and then summarized within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r summarize_by_cities}

homicide_data_summarized = homicide_data %>% 
  mutate(city_state = str_c(city, state, sep = ", ")) %>% 
  group_by(city_state) %>% 
  summarize(total_homicides = n(),
         unsolved_homicides = sum(disposition == "Closed without arrest" | disposition == "Open/No arrest")) 

```

####Part 3: Proportion of homicides unsolved for Baltimore, MD

For the city of Baltimore, MD, I used the prop.test function to estimate the proportion of homicides that are unsolved; saved the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r prop_unsolved_baltimore}
prop_unsolved_baltimore = 
  homicide_data_summarized %>% 
  filter(city_state == "Baltimore, MD")

balt_prop_estimates = 
  prop.test(x = prop_unsolved_baltimore$unsolved_homicides, 
            n = prop_unsolved_baltimore$total_homicides) %>% 
  broom::tidy() 

balt_prop_estimates[c(1,5,6)]
```

####Part 4: Proportion of homicides unsolved for each city

Below I ran prop.test for each of the cities in the dataset, and extract both the proportion of unsolved homicides and the confidence interval for each.

```{r prop_unsolved_city}
prop_unsolved_each_city = function(each_city){

  prop_unsolved = homicide_data_summarized %>% 
    filter(city_state == each_city)

  prop_estimates = prop.test(x = prop_unsolved$unsolved_homicides, 
                            n = prop_unsolved$total_homicides) %>% 
    broom::tidy() 
  
tibble(
  estimate = prop_estimates[[1]],
  upper_CI = prop_estimates[[5]],
  lower_CI = prop_estimates[[6]]
)
}
```

```{r nesting_each_city}
each_city_nest = nest(homicide_data_summarized, total_homicides:unsolved_homicides) 

each_city_nest = 
  each_city_nest %>% 
  mutate(output = map(each_city_nest$city_state, prop_unsolved_each_city)) %>% 
  unnest()

each_city_nest
```

####Part 5: Creating a plot of estimates and CIs for each city

Below I've created a plot that shows the estimates and CIs for each city. I've organized cities according to the proportion of unsolved homicides. Tulsa, AL had the lowest proportion of unsolved homicides and Chicago, IL had the highest proportion of unsolved homicides.

```{r estimate_plot}
plot_2 = each_city_nest %>%
  ggplot(aes(x = city_state, y = estimate)) + 
    geom_point(aes(reorder(city_state, estimate)), color = "BLUE") +
    geom_errorbar(aes(ymin = lower_CI, ymax = upper_CI), 
                  color = "RED", 
                  width = 0.1, 
                  alpha = 0.5) +
    labs(title = "Proportion of Unsolved Homicide for Each City",
        x = "City",
        y = "Proportion of Unsolved Homicides") + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 7))
plot_2
```

